**OptiClust: Improved method for assigning amplicon-based sequence data to operational taxonomic units**

### 2016-10-25 submission/Westcott_OptiClust_mSystems_2016.Rmd
More editing

**Figure 3. Effects of taxonomically splitting the datasets on clustering quality.** The datasets were split at each taxonomic level based on their classification using a naive Bayesian classifier and clustered using average neighbor, VSEARCH-based AGC, and OptiClust.

>>>>

**Figure 3. Effects of taxonomically splitting the datasets on clustering quality.** The datasets were split at each taxonomic level based on their classification using a naive Bayesian classifier and clustered using average neighbor, VSEARCH-based DGC, and OptiClust.
